---
title: "Manufacturing, value added (% of GDP)"
author: "teramonagi"
output: html_document
---

<style>
  iframe {
  height: 550px;
  width: 850px;
  }
</style>

This document shows "How the 'Manufacturing, value added (% of GDP)' changed over time" using R(rCharts, dygraphs packages).
```{r}
options(warn=-1)
suppressPackageStartupMessages(library(knitr))
suppressPackageStartupMessages(library(WDI))
suppressPackageStartupMessages(library(tidyr))
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(xts))
suppressPackageStartupMessages(library(zoo))
suppressPackageStartupMessages(library(dygraphs))
suppressPackageStartupMessages(library(rCharts))
suppressPackageStartupMessages(library(pipeR))
opts_chunk$set(prompt=TRUE, warning=FALSE, error=FALSE, results = "asis", comment=NA, tidy=FALSE)
#Country code(ISO-2 character, G20 + my interests)
iso2c <- c("AU", "AT", "BE", "BR", "KH", "CA", "CN", "DK", "FI", "FR", "DE", "GR", "IN", "ID", 
           "IT", "JP", "KP", "KR", "MY", "MX", "NL", "NZ", "NO", "PH", "PT", "RU", "SA", "SG", 
           "ZA", "ES", "SE", "CH", "TH", "TR", "AE", "GB", "US", "VN")
#Get data
manu <- WDI(country=iso2c, indicator='NV.IND.MANF.ZS', start=1960, end=2013)
```

To visualize data with rCharts(nPlot, NVD3), You have to write as the folloing:
(You have to be careful not to choose so much counties because it is too heavy to show)

```{r}
#rCharts(nPlot, NVD3)
data_nplot <- manu %>>% na.omit %>>% select(-iso2c) %>>%
  rename(value=NV.IND.MANF.ZS) %>>%
  mutate(value=round(value)) %>>%
  as.data.frame
nplot <- nPlot(value~year, data=data_nplot, group="country", type="lineChart")
#Default country : Japan
nplot$set(disabled = unique(data_nplot$country) %>>% (.!="Japan"))
nplot$yAxis(axisLabel="Manufacturing, value added (% of GDP)")
nplot$xAxis(axisLabel="Year")
nplot$set(height=550, width=850)
nplot$show("iframesrc", cdn=TRUE)
```
<style>iframe.rChart{ width: 100%; height: 600px;}</style>

In addition to that, I make a graph with [dygraph package](http://rstudio.github.io/dygraphs/index.html). It it a little bit difficult to understand at first sight :(
```{r}
#Make a color
#Caution：We must seem to remove the last two characters(alpha value) and name attribution
cl <- rainbow(length(iso2c)) %>% sapply(function(x)substr(x, 1, 7))
names(cl) <- NULL
#dygraph
manu %>>% select(year, country, NV.IND.MANF.ZS) %>>% na.omit %>>%
  spread(key=country, value=NV.IND.MANF.ZS) %>>% 
  as.data.frame %>>% 
  mutate(year=as.Date(as.character(year), "%Y")) %>>%
  read.zoo %>>% as.xts %>>% 
  dygraph(main="USDJPY and EURJPY charts") %>>% 
  dyHighlight(hideOnMouseOut=FALSE, highlightSeriesOpts=list(strokeWidth = 3)) %>>%
  dyLegend(show = "always", hideOnMouseOut=FALSE) %>>%
  dyOptions(colors=cl)
```


To Search the indicator of WDI function, we can use
```{r}
#Search data key
WDIsearch('manufacturing')
```